### 2023-09-20 3.Design/netlist.tex
Ädded description

>>>>

\begin{itemize}
  \item Dense layer : This is basically a \ac{VMM} so the weights are just sorted linearly in a list. The list is of size $n^2$, where $n$ is the size of the input vector. \Cref{mtrx:wei} shows the position ($i$) of the weight ($w_i$) in the matrix.
  \item \ac{LSTM} layer : An \ac{LSTM} layer contains four \acp{VMM} which can be assimilated and thus stored like a dense layer. The weights for each \ac{VMM} is then stored in a sub list.
\end{itemize}

\begin{equation}\label{mtrx:wei}
  \begin{bmatrix}
    w_{0} & w_{1} & \dots \\
    \dots & w_i & \dots \\
    \dots & w_{n^2-2} & w_{n^2-1}\\
  \end{bmatrix}
\end{equation}
